Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-22 paper/paper.tex
adding some references to V.E

\subsubsection{\Fix{Lack of }Comparison with other tools}
 \Gui{There are a few reasons that makes the comparison between Syrius and other tools \Fix{impossible}

\textbf{Tools availability.} We tried contact with authors of 5 different papers \Fix{[10][34][37][iran][bayesian]}, but got no response from them. Since their tools are not available online or at least not publicly, we could not run them.

>>>>

\subsubsection{Lack of comparison with other tools}
 \Gui{There are a few reasons that makes the comparison between Syrius and other tools impossible

\textbf{Tools availability.} We tried contact with authors of \Fix{3} different papers \cite{vollmer-etal-cics2011}\cite{muthuregunathan-etal2009}\cite{fallahi}, but got no response from them. Since their tools are not available online or at least not publicly, we could not run them.
